SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf paper: - revised the reply regarding the refinement of the Failure Monitor architecture (now footnote 2 in Section 5.2) - provided corresponding short answers to the reviewers

In this section, we present the Failure Monitor architecture from the
CubETH nanosatellite on-board software
case-study~\cite{CubETH-case-study} realised using BIP.
The architecture-based design process in BIP takes as input a set of
components providing basic functionality of the system and a set of
temporal properties that must be enforced in the final system.  For
each property, a corresponding architecture is identified
and applied to the model, thereby potentially introducing additional
coordinator components and modifying the connectors that define
synchronisation patterns among ports of components.

@@

\ERIC{\st{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components. We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}}

Figure~\ref{schema:ArchFailure:BIP} shows this refined version of the
Failure Monitor architecture used in~\cite{CubETH-case-study}.
%
The architecture consists of 2 \emph{coordinator components}
($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},
respectively), 5 \emph{dangling ports} ($\PortFail$, $\PortResume$,
$\PortTick$, $\PortReset$ and $\PortAsk$) and 5 connectors.
%
%% Contrary to standard BIP models, architectures comprise one or several
%% \emph{operand} components, whereof only the set of \emph{ports} is
%% given.  Here, the operand component is $\NameOprnd$ and its interface
%% consists of the ports $\PortResume$ and $\PortFail$.
%% The two \emph{coordinator} components\mdash $\NameCtrl$ and
%% $\NameTimer$\mdash are standard
The  \emph{behaviour} of BIP components %% insofar as they also
%% have their 
is specified by finite automata extended with
local data variables.  Transitions of these automata are labelled with
the ports of the corresponding components, Boolean guards and update
functions on local variables.  %% For instance, the loop transition
%% $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
%% in the $\NameTimer$ component is labelled by the port $\PortTick$. It
%% can be fired only when the current value of the local variable $t$ is
%% lower than $Max$.  Upon firing, this transition increments the value
%% of $t$ by $1$.  When omitted, the default guard (\resp update
%% function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
%% operator).  The constant $\mathrm{Max}$ above, is a parameter of the
%% architecture.
Although this is not visible in the figure, below we will assume that
the dangling ports $\PortFail$ and $\PortResume$ belong to the operand
component, whereas the dangling ports $\PortTick$, $\PortAsk$ and
$\PortReset$ represent actions of the environment.

>>>>

In this section, we present \Simon {a variation of} the Failure Monitor architecture from the
CubETH nanosatellite on-board software
case-study~\cite{CubETH-case-study} realised using BIP.
The architecture-based design process in BIP takes as input a set of
components providing basic functionality of the system and a set of
temporal properties that must be enforced in the final system.  For
each property, a corresponding architecture is identified
and applied to the model, thereby potentially introducing additional
coordinator components and modifying the connectors that define
synchronisation patterns among ports of components.

@@

Figure~\ref{schema:ArchFailure:BIP} shows this modified version of the
Failure Monitor architecture used in~\cite{CubETH-case-study}.\footnote{%
%
  \Simon{%
  The original CubETH case study \cite{CubETH-case-study} focused on
  the possibility of assembling a model of a complex software system
  in a systematic way by applying architectures to discharge
  individual system requirements.  Here, we are more interested by the
  properties of the Failure Monitor architecture by itself.  For that
  reason, we provide a modified version, in particular decomposing the
  coordinator into a Controller and a Timer, altering them to allow
  more flexibility in the acceptable behaviours.  In other words, this
  modification enforces essentially the same properties, while
  discarding less acceptable behaviours.
  }
%
} The architecture consists of 2 \emph{coordinator components}
($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},
respectively), 5 \emph{dangling ports} ($\PortFail$, $\PortResume$,
$\PortTick$, $\PortReset$ and $\PortAsk$) and 5 connectors.
%
%% Contrary to standard BIP models, architectures comprise one or several
%% \emph{operand} components, whereof only the set of \emph{ports} is
%% given.  Here, the operand component is $\NameOprnd$ and its interface
%% consists of the ports $\PortResume$ and $\PortFail$.
%% The two \emph{coordinator} components\mdash $\NameCtrl$ and
%% $\NameTimer$\mdash are standard
The  \emph{behaviour} of BIP components %% insofar as they also
%% have their 
is specified by finite automata extended with
local data variables.  Transitions of these automata are labelled with
the ports of the corresponding components, Boolean guards and update
functions on local variables.  %% For instance, the loop transition
%% $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
%% in the $\NameTimer$ component is labelled by the port $\PortTick$. It
%% can be fired only when the current value of the local variable $t$ is
%% lower than $Max$.  Upon firing, this transition increments the value
%% of $t$ by $1$.  When omitted, the default guard (\resp update
%% function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
%% operator).  The constant $\mathrm{Max}$ above, is a parameter of the
%% architecture.
Although this is not visible in the figure, below we will assume that
the dangling ports $\PortFail$ and $\PortResume$ belong to the operand
component, whereas the dangling ports $\PortTick$, $\PortAsk$ and
$\PortReset$ represent actions of the environment.
